### 2016-03-14 paper/algorithm.tex
hang
Hang

Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
   Fusion (SF) architecture and its relationships to existing methods. The
 bottom right example shows the general SF architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the
 parameters (e.g., the left two examples in the bottom row).
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
% The left two examples at the bottom are other Swarm fusion
% architectures with some restrictions, to be used for evaluations later.
 %
 It is easy to verify that existing popular MRF inference methods such
 as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{fusion_moves_for_markov_random_field_optimization},
 Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, or Hierarchical
 Fusion~\cite{delong_hierarchical_fusion}, are all special cases of
 SF.}
\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which threads
conduct multi-way fusion of either solution proposals, or some concurrent solutions, or both (i.e.,
$\alpha\ne 0, \beta \ne 0$).
%
And the energy is not submodular
in general, for which effective inference techniques such as
TRW-S~\cite{TRW-S,opengm} exist.
%, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
%compatible inference techniques can be used~\cite{opengm}.
However, if one knows that a certain fusion step is a binary fusion with
submodular energy, one can use
graph-cuts~\cite{alpha_expansion}. If a certain fusion step is a
binary fusion with non-submodular energy, one can use
QPBO~\cite{second_order_stereo}.
%
Note that the threads appear synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See
Algorithm~\ref{algorithm:sf}). The asynchronous computing further unleashes the power of parallism.
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  %\State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Generate $\alpha$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  %\State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

>>>>

Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
   Fusion (SF) architecture and its relationships to existing methods. The
 bottom right example shows the general SF architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the
 parameters (e.g., the left two examples in the bottom row).
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
% The left two examples at the bottom are other Swarm fusion
% architectures with some restrictions, to be used for evaluations later.
 %
 It is easy to verify that existing popular MRF inference methods such
 as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{fusion_moves_for_markov_random_field_optimization},
 Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, or Hierarchical
 Fusion~\cite{delong_hierarchical_fusion}, are all special cases of
 SF.}
\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which threads
conduct multi-way fusion of either solution proposals, or some concurrent solutions, or both (i.e.,
$\alpha\ne 0, \beta \ne 0$).
%
For general non-submodular energy, we use TRW-S~\cite{TRW-S, opengm} for inference.
%% And the energy is not submodular
%% in general, for which effective inference techniques such as
%% TRW-S~\cite{TRW-S,opengm} exist.

%, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
%compatible inference techniques can be used~\cite{opengm}.
However, if one knows that a certain fusion step is a binary fusion with
submodular energy, one can use
graph-cuts~\cite{alpha_expansion}. If a certain fusion step is a
binary fusion with non-submodular energy, one can use
QPBO~\cite{second_order_stereo}.
%
Note that the threads appear synchronized in the figure only for
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the solution pool (See
Algorithm~\ref{algorithm:sf}). The asynchronous computing further unleashes the power of parallism.
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  %\State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Generate $\alpha$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  %\State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

### 2016-03-14 paper/optical_flow.tex
Hang

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. The same
configurations as in the stereo problem have been used for optical flow,
that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.

>>>>

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
have been evaluated against the competing methods. The similar
configurations as in the stereo problem have been used for optical flow,
that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.\hang{seems to have some repeating and incomplete sentences here}

### 2016-03-14 paper/stereo.tex
Hang

\section{Swarm Fusion instantiation}
We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantify the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}. For some problems,
we have further limited the capabilities of SF on purpose, to enable
effective and fair comparative evaluations. We now explain the details
of the three problems.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it
slow due to the overhead.\hang{Don't quite understand this
  sentence. Does the ``dominant'' means running time or energy? In my
  experiments, unary terms are pre-computed and are not counted into
  the running time} Therefore, we have chosen standard sequential
$\alpha$-expansion, Parallel Alpha Expansion(PAE)~\cite{delong} and
Hierarchical Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion} with graph-cuts optimization as
the competing methods.

@@

%
%
%
%
To make the comparison simple, we restrict our proposal generation to
be constant-label proposals. Graph-cuts is used in fusing a
constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\section{Swarm Fusion instantiation}
We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantify the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}.
%% For some problems, we have further limited the capabilities of SF
%% on purpose, to enable effective and fair comparative
%% evaluations. We now explain the details of the three problems.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it
slow due to the overhead.\hang{Don't quite understand this
  sentence. Does the ``dominant'' means running time or energy? In my
  experiments, unary terms are pre-computed and are not counted into
  the running time} Therefore, we have chosen single thread Alpha
Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical
Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
with graph-cuts optimization as the competing methods.

@@

%
%
%
%
To make the comparison simple, we restrict our proposal generator
in each thread to only generate constant-label proposals within a
subset of all labels. Graph-cuts is used in fusing a constant-label
proposal as the energy is submodular. QPBO is used in fusing a
different solution from another thread as the energy is typically
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
